\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \input{glyphtounicode}
\usepackage{comment}
\usepackage{changepage}
\pdfgentounicode=1

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{5pt}

% Style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-0.2cm}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom Commands
% \newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeItem}[1]{\item[$\bullet$]\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{\href{#2}{#1}} $|$  \textbf{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\LARGE Ashish Kushwaha} \\
  \vspace{2pt}
  \textbf{\normalsize Software Development Engineer} \\
  \vspace{2pt}
  \small
  \href{https://github.com/ashish-kus}{github.com/ashish-kus} $|$ 
  \href{mailto:ashish.kus2408@gmail.com}{ashish.kus2408@gmail.com} $|$ 
  \href{https://www.linkedin.com/in/ashish-kushwaha2408}{linkedin.com/in/ashish-kushwaha2408} $|$ 
  \href{tel:+917525874187}{+91 7525874187}
\end{center}
\vspace{-8pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Gautam Buddha University}{Greater Noida, Uttar Pradesh}
    {Bachelor of Technology in Computer Science and Engineering , CGPA: 8.2}{08/2020 -- 06/2024}
  \resumeSubheading
    {Gautam Buddha University}{Greater Noida, Uttar Pradesh}
    {M.Tech in CSE with Specialization in Software Engineering, CGPA: 8.5}{08/2024 -- 06/2025}
\begin{comment}
  \resumeSubheading
    {Narayana IIT Academy, Raviryala}{Hydrabad, Telangana State}
    {Intermediate – Physics, Chemistry, Mathematics: 88\%}{March 2017 -- March 2019}
\end{comment}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Software Development Engineer | Arial Labs}{06/2024 – 05/2025}
    {California, Remote}{}
    \resumeItemListStart
      \resumeItem{Independently developed the company’s core product MVP integrating Claude API  with AWS serverless backend services.}
      \resumeItem{Set up CI/CD pipelines, monitoring, and infrastructure automation using Docker, GitHub Actions, and Kubernetes.}
      \resumeItem{Built scalable SaaS architecture ensuring scalability and availability within 3 months, acquiring early customer acquisition.}
    \resumeItemListEnd

  \resumeSubheading
    {Samsung Innovation Campus — Artificial Intelligence Training}{ 06/2024 – 09/2024}
    {Greater Noida, Onsite}{}
    \resumeItemListStart
      \resumeItem{Completed comprehensive training on Artificial Intelligence covering Machine Learning and Data Analytics.}
      \resumeItem{Developed models and fine-tuned LLM and Gen AI models using Python, TensorFlow, PyTorch, flux and more.}
      \resumeItem{Optimized training performance by managing system resources, GPU utilization, and process scheduling on Linux.}
    \resumeItemListEnd


\begin{comment}
  \resumeSubheading
    {Web Developer Intern | SOMHH}{Nov 2023 – Jan 2024}
    {Delhi, Remote}{}
    \resumeItemListStart
      \resumeItem{Developed a static fundraising website using Svelte and Bootstrap, significantly enhancing digital presence and outreach.}
      \resumeItem{Integrated Razorpay and Stripe payment gateways, streamlining the donation process and improving user experience.}
    \resumeItemListEnd
\end{comment}

    \resumeSubheading
    {Web Developer Intern | Gautam Buddha University}{03/2023 – 06/2023}
    {Greater Noida, in campus}{}
    \resumeItemListStart
      \resumeItem{Developed a MERN stack webapp to manage and track job applicants, improving recruitment efficiency by 30\%.}
      \resumeItem{Implemented 5+ REST APIs and integrated MongoDB for robust and scalable data management.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {HireLift}{https://chromewebstore.google.com/detail/hirelift/gchcmaknjamkfbcgbafcchcglpeagidi}{Chrome Extension APIs, AWS, WebSockets and REST APIs.}{}
    \resumeItemListStart
      \resumeItem{AI-powered Chrome extension used by 10+ hiring managers across 60+ interviews to streamline technical evaluations.}
      \resumeItem{Integrates with 4+ platforms to analyze live captions and JD–CV uploads, generating real-time questions.}
      \resumeItem{Generates post-interview summaries with tech skills, JD alignment, and key candidate insights via the dashboard.}
    \resumeItemListEnd

\begin{comment}
  \resumeProjectHeading
  {Mtag Gen}{https://github.com/ashish-kus/SEO_metaTag_generater}{Meta Tag Generator $|$ HTML, CSS, JavaScript, Netlify}{}
  \resumeItemListStart
    \resumeItem{Developed an intuitive web app to preview and generate SEO meta tags (HTML, Open Graph, Twitter Cards) for websites.}
    \resumeItem{Allows users to fetch metadata from a URL or manually input values to create optimized tags in seconds.}
    \resumeItem{Deployed on Netlify and featured a clean UI/UX focused on simplicity, accessibility, and quick SEO validation.}
  \resumeItemListEnd

\resumeProjectHeading
  {Pixelify}{https://pixelify.netlify.app/}{React, Tailwind CSS, Sanity.io, OAuth, Netlify, Git/GitHub}{}
    \resumeItemListStart
      \resumeItem{A full-stack Pinterest-style image sharing platform with dynamic pin uploads, user authentication, and real-time updates.}
      \resumeItem{Includes Masonry layout, category filtering, pin detail view with comments, and secure pin creation with upload previews.}
    \resumeItemListEnd

\resumeProjectHeading
  {Batfetch}{https://github.com/ashish-kus/batfetch}{Linux Battery Information Analyzer $|$ Shell, JSON, CLI, Makefile, AUR}{}
    \resumeItemListStart
      \resumeItem{Command-line tool inspired by \texttt{pfetch}, display detailed battery information in a clean format with optional JSON output.}
      \resumeItem{Supports multiple installation methods including AUR, manual install via Makefile, and Nix Flake.}
      \resumeItem{Open source project with 4 open, 4 closed and 2 closed, 1 open pull request. This is avalable on Arch user Repositories.}
    \resumeItemListEnd

    
\resumeProjectHeading
{Waybar-Hotspot}{https://github.com/ashish-kus/waybar-hotspot}{ Bash, Zenity, create\_ap}{}
  \resumeItemListStart
    \resumeItem{Waybar module for monitoring and managing Wi-Fi hotspot status with graphical prompts using Zenity.}
    \resumeItem{Supports custom configurations for create\_ap and QR code display in tooltips for easy access.}
  \resumeItemListEnd

\end{comment}

\resumeProjectHeading
  {Huegen – Systems Theme Generator}{https://github.com/ashish-kus/huegen}{ C++17, OpenCV, linux}{}
    \resumeItemListStart
      \resumeItem{A C++17 tool to extract dominant colors from images using K-means clustering and LAB-based perceptual filtering.}
      \resumeItem{Template engine to auto-generate theme files suporting 4+ color formats and 10+ application by default.}
      \resumeItem{Designed a modular architecture with customizable templates and automation hooks for instant theme application.}
    \resumeItemListEnd


  \resumeProjectHeading
  {Research Papper}{https://github.com/ashish-kus}{Adaptive Task-Based CPU Scaling for Efficient Power Allocation in Edge Computing}{}
    \resumeItemListStart
      \resumeItem{Proposed a lightweight, task-based CPU frequency scaling framework and daemon-driven architecture for reduce power consumption and thermal stress in IoT devices.}
      \resumeItem{Achieved 90\% reduction in CPU frequency variation and 6–8\% lower average temperature on Raspberry Pi 3B.}
      \resumeItem{Published in Springer LNCS, CVR 2025, by NIT Goa, sponsored by the Soft Computing Research Society.}
  \resumeItemListEnd


\resumeSubHeadingListEnd

\section{Technical Skills}

\begin{adjustwidth}{0.25in}{0in}
  \textbf{Programming Languages}: C++, C, Bash, JavaScript, Python, Lua, LaTeX, HTML, CSS.\\
  \textbf{Frameworks \& Libraries}: ReactJS, FXTUI, TailwindCSS, Chrome Extensions, YAML.\\
  \textbf{Databases}: MySQL, MongoDB.\\
  \textbf{Tools}: SEO, AWS, QEMU, Linux, Git, GitHub Actions, Docker, Nginx, Vagrant.\\
  \textbf{Soft Skills}: Effective Communication, Problem-Solving, Leadership, Adaptability, Team Collaboration.
\end{adjustwidth}


%-----------COMMUNITY-----------
\section{Certification, Publication \& Achievements}
\resumeItemListStart
  \resumeItem{Published research paper titled “Adaptive Task-Based CPU Scaling for Efficient Power Allocation in Edge Computing” at CVR2025. The paper will be part of the Springer Book Series: Lecture Notes in Networks and Systems.}
  \resumeItem{Introduction to Linux (LFS101) by The Linux Foundation, covering core Linux systems and essential fundamentals.}
  \resumeItem{Earned the Hacktoberfest 2024 badge and published multiple packages on the Arch User Repository (AUR).}
  \resumeItem{Earned the Oracle Cloud Infrastructure Essentials badge, gaining hands-on experience with core OCI services and architecture.}
\resumeItemListEnd

\end{document}

